Neural Style Transfer on Text\\Project Report One

### 2017-11-12 dl-style-transfer/reports/src/project_report_another_one.tex
Updated project report

	\item [Ryan Butler]
		Further research into KATE, Discrete Autoencoders, and other methods we may be interested in incorporating into our model.

>>>>

	\item [Ryan Butler]
		Further research into KATE, Discrete Autoencoders, ResNet, and Inception/Google to search
		for methods we may be interested in incorporating into our model.
